Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-04 ltx/data_paper/DataPaper.tex
edit to introduction

Another recent approach for large scale neural networks based on graph theory \cite{Albert2002,Bang-Jensen2010}, employs a realistic anatomical connectivity from CoCoMac data base \cite{Kotter2004} to model resting state activity in the brain \cite{Ghosh2008,Deco2009} where each node in the network is modelled by physiologically reasonable neural population model of their internal dynamics. They perform a stability analysis of the network in terms of total connectivity and time delays in the presence of noise. Such approach has a potential to model a virtual brain which can incorporate data from individual patient, giving insights into how patient specific features can affect its large scale neural dynamics \cite{Jirsa2010,Deco2010}.

>>>>

Another recent approach uses graph theory \cite{Albert2002,Bang-Jensen2010} for large-scale neural networks and employs realistic anatomical connectivity from the CoCoMac database \cite{Kotter2004} to model the brain's resting state activity \cite{Ghosh2008,Deco2009}. Each node in the network is described by a physiologically reasonable neural population model of their internal dynamics. The authors perform stability analysis on the network based on total connectivity and time delays in the presence of noise. Such an approach has the potential to model a virtual brain which can incorporate data from individual patients, giving insights into how patients' specific features can affect its large-scale neural dynamics \cite{Jirsa2010,Deco2010}.
